---
title: "PROJECT 1 Part II"
author: "Ruoying jiang, Shenqian Chen"
output: slidy_presentation
---

## Bullets:

- Bullet 1 Combine meteorological data with the average pm2.5 per day data in 2015 for Beijing
- Bullet 2 Fit regression model without days indicate significant high values of pm2.5(>250)
- Bullet 3 Do specific reaserch&analysis for days that pm2.5>250 (outliers)

-Data Source: http://www.wunderground.com/history/ (Meteorological data)  
              http://www.stateair.net/web/historical/1/1.html (PM2.5 data)

## R Code and Output 1 
####(1)First,Fit linear regression for mean(pm2.5) versus meterological variables with lag factor.  
```{r}
beijing<-read.csv("pmn.csv",header = T)
require(dplyr)
require(ggplot2)
new.dd<-beijing%>%filter(mean.pm<250)
fit1<-lm(mean.pm~lag(mean.pm,1)+Mean.TemperatureF+MeanDew.PointF+Mean.Humidity+Mean.VisibilityMiles+Mean.Wind.SpeedMPH,data=new.dd)
summary(fit1)
``` 
* The average PM2.5 for each day: Negative Relationship with Mean.Temperature, Mean.Humidity,Mean.VisibilityMiles, Mean.Wind.SpeedMPH.  
* The average PM2.5 for each day: positive Relationship with Mean(PM2.5) one day bofore, MeanDew.point. 

## Plots(for data without outliers):
```{r, echo=FALSE}
ggplot(data=beijing,aes(x=1:365,y=mean.pm))+geom_point()+geom_hline(yintercept=250,color="red")+ggtitle("avarage pm2.5 each day in 2015")
ggplot(fortify(fit1),aes(x=.fitted,y=.resid)) + geom_point() + geom_hline(yintercept=0)+geom_smooth(se=F,lwd=1)+ggtitle("residuals Plot")
new.dd$fit1 <- predict.lm(fit1, newdata=new.dd)
gg <- ggplot(new.dd)+geom_point(aes(x=mean.pm, y =fit1), size = 2, color = "blue")
gg + geom_smooth(data=new.dd, aes(x=mean.pm, y=fit1), size = 1.5, color = "red", se = TRUE, method="lm")+ggtitle("fitted model of pm2.5")
```

## R Code and Output 2  
####(2)Employ daily data to analysize outliers(mean(pm2.5)>250)
```{r}
out.dd<-beijing%>%filter(mean.pm>250)
out.dd%>%select(Month,Day,mean.pm)

``` 
